\clearemptydoublepage

\phantomsection
\addcontentsline{toc}{chapter}{Outline and Overview of the document}

\begin{center}
	\huge{Outline and Overview}
\end{center}




%--------------------------------------------------------------------
\section*{Purpose of the document}
The purpose of this document is to describe the \emph{CAD-integrated Topology Optimization} software tool along with the theoretical background it relies on.
%
%This document describes the overall process of \textit{Topology Optimization} with the following conversion of an obtained surface back to CAD. It includes the required theoretical background, a brief description of external libraries used within the project and the detailed information about algorithms developed for the implementation of the functionality not provided by open source libraries available.

%--------------------------------------------------------------------
\section*{Document overview}
The document is arranged in chapters. The current and first chapter provides an overview of the document structure, brief introduction to the topic, motivation and administrative details of the project. The second chapter provides a thorough review of the theory and techniques used within the project.
\\
\\
%--------------------------------------------------------------------
\noindent {\scshape Chapter 1: Introduction}  \vspace{1mm}

\noindent  This chapter presents an overview of the motivation behind \textit{CAD--integrated Topology Optimization}, including the current state of the art. It also provides general organizational information about the project execution, such as timeline and structure.
 \\


%--------------------------------------------------------------------
\noindent {\scshape Chapter 2: Background theory}  \vspace{1mm}

\noindent This chapter introduces the theoretical background for the implementation of the \textit{CAD--integrated Topology Optimization} tool. It consists of the five parts, describing the essential steps of the \textit{Topology Optimization} pipeline. Furthermore, the detailed description of algorithms and libraries used in each step is given.
\\

\noindent {\scshape Chapter 3: Implementation}  \vspace{1mm}

\noindent This chapter provides details on the implementation and structure of the \textit{CAD--integrated Topology Optimization} tool itself. The different parts of the \textit{Topology Optimization} pipeline are presented along with underlying implementation details.
\\