\clearemptydoublepage

\phantomsection
\addcontentsline{toc}{chapter}{Outline and Overview of the document}

\begin{center}
	\huge{Outline and Overview}
\end{center}




%--------------------------------------------------------------------
The purpose of this document is to describe the implementation details of the \emph{CAD-integrated Topology Optimization} software tool along with the theoretical background it relies on. The document is arranged in chapters, covering introduction to the field and the project, background theory and parts of implementation. The chapters are described in more detail below.
\\
\\
%--------------------------------------------------------------------
\noindent {\scshape Chapter 1: Introduction}  \vspace{1mm}

\noindent  This chapter presents an overview of the motivation behind \emph{CAD-integrated Topology Optimization}, including the current state of the field. It also provides general organizational information about project execution, timeline and structure.
\\


%--------------------------------------------------------------------
\noindent {\scshape Chapter 2: Background Theory}  \vspace{1mm}

\noindent This chapter introduces the theoretical background for the implementation of the \emph{CAD-integrated Topology Optimization} tool. It consists of five parts, each describing essential background of the topology optimization pipeline. Furthermore, detailed description of selected algorithms used in each step is given.
\\

\noindent {\scshape Chapter 3: Implementation}  \vspace{1mm}

\noindent This chapter provides details on the implementation and structure of the \emph{CAD-integrated Topology Optimization} tool itself. The different parts of the topology optimization and surface-fitting pipeline are presented along with underlying implementation details.
\\ 

\noindent {\scshape Chapter 4: Results}  \vspace{1mm}

\noindent This chapter presents the implemented product of the \emph{CAD-integrated Topology Optimization} tool which the user experiences in terms of a graphical user interface. Additionally, three different test cases are described to show the performance of the integrated tool-chain.
\\

\noindent {\scshape Chapter 5: Summary and Future Work}  \vspace{1mm}

\noindent In the final chapter a summary of the whole project is provided. Weak spots of the algorithms are described including an outlook on areas where future optimization of the product is considered promising.  


\begin{comment}
\\
\noindent {\scshape Chapter 4: Summary and future work}  \vspace{1mm}

\noindent The final chapter summarizes the current status of the project and enumerates objectives for the next phase. \todourgent{Check if consistent with what the Gods want. -Saumi}
\\
\end{comment}
\tododone{Severin: Add chapter 4 and 5; Please proofread}
