\subsection{Fairness Functional}%maybe change title
Aside from recognising discontinuities in the first derivative (kinks), the human eye is usually able to recognise large values in curvature, that is, properties depending on the second derivatives of a surface. For example, we can have a surface that is entirely continous in the first derivative of the surface, that also has large wiggles and sharp turns, that on a small scale are smooth, but do not seem so on the large scale. %maybe example of a gaussian with very small variance? 
\todointernal[author=Erik]{mention that it's called fairness because they're nice to look at}
To give a measure for this, one can for example use the bending energy of a thin plate, which depends on the squared magnitude of the second derivatives. In the special case of a rectangular patch, parametrized by $u,v\in \left[0,1\right]$, we can easily integrate this over the whole area. The energy can then be expressed as a functional of $\vec{S}$,

\begin{equation}
\label{eq:fairness}
E_{patch}\left[\vec{S}\right] = 
\int\limits_0^1 \int\limits_0^1
\left(
(\frac{\partial^2}{\partial u^2 }\vec{S}(u,v))^2
+ 2 
(\frac{\partial^2}{\partial u\partial v} \vec{S}(u,v))^2
+
(\frac{\partial^2}{\ v^2}\vec{S}(u,v))^2
\right)
\text{d}u\text{d}v
\end{equation}
One case in which this equation can be simplified is when we have explicit definitions of the surface. For example, for the rectangular \Bez tensor product surface curves in \autoref{subsec:paracurves}, we express the surface as a weighted sum of polynomials in $u$ and $v$ (see \autoref{eq:bezsurface} for a reminder). For a \Bez surface of order $N$, with $N+1$ points $\vec{p}_{i,j}$ in each direction, we can thus reexpress \autoref{eq:fairness} as coefficients times a dot product 
\begin{equation}
\label{eq:faireqsum}
E_{fair} =  \sum\limits_{i_1,j_1=1}^{N+1} \sum\limits_{i_2,j_2=1}^{N+1} \left( c_{(i_1,j_1),(i_2,j_2)}^{uu} + 2c_{(i_1,j_1),(i_2,j_2)}^{uv} + c_{(i_1,j_1),(i_2,j_2)}^{vv} \right) \vec{p}_{i_1,j_1} \cdot\vec{p}_{i_2 ,j_2} 
\end{equation} 
where the coeficcients $c_{(i_1,j_1),(i_2,j_2)}^{st}$ are obtained by of multiplying out the squares in the energy functional, inserting the definitions of the Bernstein polynimials $b_{i}^N(u)$:
\begin{equation}
c_{(i_1,j_1),(i_2,j_2)}^{st} = 
\int\limits_0^1 \int\limits_0^1 \frac{\partial^2}{\partial s \partial t} \left[b_{i_1}^N(s) b_{j_1}^N(t)\right]\frac{\partial^2}{\partial s \partial t} \left[ b_{i_2}^N(s) b_{j_2}^N(t)\right]
\text{d}s\text{d}t
\end{equation}
\todointern[author=Erik]{maybe move this following part to LeastSquares?}
Although this is already very much simpler to evaluate, given one already has the coefficients $c_{(i_1,j_1),(i_2,j_2)}$, we can do a further reformulation by reindexing $(i,j)$ to $k$ where $k$ goes from $1$ to $(N+1)\times(N+1)$. By forming a vector $P_{patch}$ containg all the points as 3-dimensional entries, we can then reexpress \autoref{eq:faireqsum} as a vector-matrix-vector product:
\begin{align*}
\phantom{=}& \sum\limits_{i_1,j_1=1}^{N+1} \sum\limits_{i_2,j_2=1}^{N+1} c_{(i_1,j_1),(i_2,j_2)} \vec{p}_{i_1,j_1} \cdot\vec{p}_{i_2 ,j_2} =
\\
=& \sum\limits_{k_1=1}^{(N+1)^2} \sum\limits_{k_2=1}^{(N+1)^2} c_{k_1,k_2} \vec{p}_{k_1} \cdot\vec{p}_{k_2} =
\\
=& P_{patch}^T C_{patch}^{fair} P_{patch}
\end{align*}
Now, since we know the original expression of $E_{fair}$ and the contribution stemming from each point $\vec{p}_{i,j}$, we know the matrix $C_{patch}^{fair}$ to be positive semi-definite and symmetric. Hence, it should be diagonalizable by an orthogonal matrix, and have only nonnegative eigenvalues. Thus, expressing $C_{patch}^{fair} = S^T \Lambda S$, we end up with:
\begin{align*}
E_{fair} =& P_{patch}^T C_{patch}^{fair} P_{patch} =
\\
=&  P_{patch}^T S^T \Lambda S P_{patch} = 
\\
=& P_{patch}^T S^T \Lambda^{\frac{T}{2}}\Lambda^{\frac{1}{2}} S P_{patch} =
\\
=& \left[\Lambda^{\frac{1}{2}} S P_{patch}\right]^T\left[\Lambda^{\frac{1}{2}} S P_{patch}\right] =
\\
=& \norm{\Lambda^{\frac{1}{2}} S P_{patch}}^2
\end{align*}
which allows us to express and calculate the thin plate energy using a matrix-vector product and a squared norm.

Since surfaces with low curvatures and therefore softer curves are typically considered more pleasing to the eye, the functional in \autoref{eq:fairness} is typically named \emph{fairness functional}.\todointern[author=Erik]{move this further up}
%%plotline: 
%as well as smoothness, curvature is important
%for quadratic parametric patch, can express curvature by thin-plate energy functional as was done in [eck-hoppe]
%we notice here that for Bezier curves, we express the \vec{S} surface as polynomials*surface points, which we can integrate analytically
%AND: this gives us a quadratic polynomial in the control points of the patch, with a lot of coefficients
%we express this as the norm in a matrix-vector thingy:
% <from here in LSQ section> and this we can then find the eigenvectors for
% which let us express this as a sum of squares of coefficients*bezier points, (just like we wanted.)


\begin{align}
\vec{d}_k = & \sum\limits_{i,j=1}^{N,M} \c(u_k,v_k)_{i,j} \lsControlPointi{i,j}
\\=& C_k (u_k,v_k)P
\end{align}
\begin{align}
\vec{p}_{p} &= \sum\limits_{l} c^{PS}_{p,l} \vec{v} 
\\
&=C_k^{PS}V
\end{align}



\begin{equation}
\label{eq:fairness-sum}
E_{fair} = \sum\limits_{\text{all quads}}E_{fair,quad}
\end{equation}
\begin{equation}
\norm{D - \left[ C(\vec{u},\vec{v}) C^{PS} \right] V }^2 + \lambda \norm{0 - C^{fair} V }^2
\end{equation}

