\subsection{Surface reconstruction}
\todo[inline]{Benni: put discussion from schemes here}

\subsubsection{Discussion \ac{MC}}
\todo[inline]{discussion makes more sense after the NURBS part.}
\todo[inline]{needs to be formulated}
Pro:
\begin{itemize}
\item produces proper \todo{what does proper mean?} surfaces
\item very simple
\end{itemize}
Contra:
\begin{itemize}
\item triangles
\item no feature detection (explicit detection with extended MC)
\item very many faces (at least in basic implementation)
\end{itemize}

\subsubsection{Manifold \ac{DC}}
Since we want to deduce a first estimate for the topology of the \ac{NURBS} surface output of our \ac{CADTopOpt} tool, non-manifold surfaces cannot be accepted\footnote{Surfaces consisting of smoothly connected \ac{NURBS} \acp{patch} are always manifold surfaces. Therefore we cannot start with a non-manifold surface and assume we will end up with a manifold surface.}. We implemented a remeshing procedure for generating manifold surfaces out of non-manifold surfaces. This procedure considers the different occurring patterns of non-manifold edges and resolves them in a proper way. 
\todo[inline]{2D pictures!!!}

\subsubsection{Topology--safe adaptivity \ac{DC}}
\todo[inline]{Benni: this is a outlook, remove, put into comment.}
Implementing this feature in \ac{DC} will be one of our major goals in the future. Whether adding adaptivity to the basic \ac{DC} algorithm will destroy the property of \ac{DC} only generating \acp{quad} by introducing \acp{tri}, is going to be part of our future research.

\subsubsection{Discussion \ac{DC}}
\todo[inline]{discussion makes more sense after the NURBS part.}
\todo[inline]{poorly written...}
\ac{DC} generates \acp{quad} instead of \acp{tri} and therefore fits better to the rectangular topology of \ac{NURBS}. The possibility of making \ac{DC} an adaptive algorithm is another advantage.
Since we do not rely on first order Hermite data and the minimization of the \ac{QEF} but just on a very simple averaging procedure, we loose one of the main advantages of \ac{DC}, namely the ability to represent sharp features. But we do not care about sharp features in the context of topology optimization. 
The main disadvantage of \ac{DC} is that it is not always generating manifold surfaces. Our approach of solving this issue by remeshing is more a hack than a real solution to the problem.